\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 scam.tex
.

>>>>

\begin{example}[Van der Pol Oscillator]

% \inclfig[width=0.95\linewidth]{vdp_cont_traces.pdf}{Van der
% Pol: continuous trajectories. Red and green boxes indicate unsafe and
% initial sets.}{vdp-cont}
%Simulations generated using uniformly random samples are shown in
%    \figref{vdp-cont}.

\inclfig[width=0.95\linewidth]{vdp_abs.pdf}{The discovered
abstraction $\epsilon=0.2$. Red cells are unsafe cells and green cells are
initial cells.}{vdp-abs}

We use the Van der Pol oscillator benchmark
from~\cite{zutshi2014multiple} to demonstrate our falsification
approach. We want to check the property $P_3$, indicated by
the red box, given the initial set indicated by the green box. The
abstraction is defined by $\epsilon=0.2$, which results in an
evenly gridded state-space, where each cell is of size $0.2 \times
0.2$ units. $ScatterAndSimulate$ is then used to construct the
abstraction, using $2$ samples per cell and the time step
$\Delta = 0.1s$. The result is plotted in ~\figref{vdp-abs}.

% \mypara{Discover}: Using scatter-and-simulate, enumerate a finite number
%     of cells (vertices) and the relations (edges) of the graph
%     $\scr{H}(0.1)$. Associate the set of generated trajectory
%     segments with their respective originating cells using a map $\ds:C
%         \mapsto \setof{(\vx,\vx') |\vx \in C}$. The discovered
%     abstraction is show in \figref{vdp-abs}. The red cells
%     are unsafe and green cells are initial cells.
\end{example}
